---
title: "CE2 Moruzzi Taddei"
author: "Chiara Moruzzi, Federico Taddei"
date: "2022-12-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## TASK 1

When we tryed to open the /robots.txt page for the blog beppegrillo.it didn't work, the result was "404 Not Found". This means that the blog doesn't have any restrictions for crawlers who want to download data from it. Next, in order to still be polite, we can download data from the web page but identifying ourselves first and using the `Sys.sleep()` function not to overload the webpage.

## TASK 2

First we download the web page identifying ourselves and using the package RCurl:

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
url <- "https://beppegrillo.it/un-mare-di-plastica-ci-sommergera/"
email <- "icotaddei@gmail.com"
agent <- R.Version()$version.string
user_id <- c(From = email, `User-Agent` = agent)

web_page <- RCurl::getURL(url=url, httpheader= (user_id))
```
## TASK 3

To download all the links in the web page we used the following function from XML: `all_link = XML::getHTMLLinks(web_page, externalOnly = T)`. To keep only the links the redirect to posts we used the regular expression "^https://beppegrillo\\.it/[^category].+[^jpg]$" as a pattern inside the function `str_subset`. Then we extracted all the selected links and put them inside a dataframe. the last line of code shown here below is necessary to remove duplicates (function `distinct ()`)

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
library(XML)
library(stringr)
library(tidyverse)

blog="^https://beppegrillo\\.it/[^category].+[^jpg]$"
links_post = all_link %>% 
  str_subset(blog)
links_post %>% 
  str_extract(all_link)

df_BG_posts = tibble(links_post)

clean_df_BG = distinct(df_BG_posts)
```

## TASK 4

First we created a combined character string which contains all the pages' URLs in Beppe Grillo's "Archivo 2016" (there are 47 pages). The URL is "https://beppegrillo.it/category/archivio/2016/page/" and varies from page 1 to page 47 (page/2/ page/3/ ... page/47/). For page 1 the URL is simply "https://beppegrillo.it/category/archivio/2016/" without specifying the number of the page.

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
links_arc <- str_c("https://beppegrillo.it/category/archivio/2016/page/", 1:47)
```

Next, to download all the pages of the linked posts we created our `download_pollitely()` function and also a new directory to store them. To iterate the function for each single page we had to use the for loop, and apply the function `download_pollitely()` over and over. We used a `Sys.sleep()` of 0.5 seconds not to overload the server and to avoid being banned from the website.

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}

download_politely <- function(from_url, to_html, my_email, my_agent = R.Version()$version.string) {
  
  require(httr)
  
  stopifnot(is.character(from_url))
  stopifnot(is.character(to_html))
  stopifnot(is.character(my_email))     # Only character strings are allowed
  
  beppe_req <-httr::GET(url = links_arc[i],   # GET function for all the pages
                        add_headers(
                          From = email, 
                          `User-Agent` = R.Version()$version.string
                        )
  )
  
  if (httr::http_status(beppe_req)$message == "Success: (200) OK") {
    bin <- content(beppe_req, as = "raw")
    writeBin(object = bin, con = to_html)
  } else {
    cat("Houston, we have a problem!")
  }
}

```

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
for (i in seq_along(links_arc)) {
  cat(i, " ")
  download_politely(from_url = links_arc[i], 
                    to_html = here::here("archivio2016", str_c("page_",i,".html")), 
                    my_email = email)
  
  Sys.sleep(0.5)
}
```

Lastly we scraped the main text of each single linked post's webpage, for a total of more than 350 posts. If an article doesn't contain any text the result in the list is `" "`. To scrape the main text we used `lapply()` to apply the functions `read_html()`, `html_elements()` and `html_text()` to all the posts in the folder "Post archivio 2016".

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
scrape_363 <- list.files(here::here("Post archivio 2016"), pattern="*.html", full.names = TRUE)

main_text = lapply(scrape_363, function(x) {
  read = read_html(x) %>% 
    html_elements(css = "p") %>% 
    html_text(trim = TRUE)
```


## TASK 5

To crawl in the field of computer science means to collect data from the Internet. Web spiders, or web crawlers, are programs that collect large amounts of data from the internet at the same time through hyperlinks methodically and automatically by browsing and downloading web pages. When a web crawler is used to download web pages and extract data from them simultaneously it is called a web scraper.

In task 4 to scrape the beppegrillo.it blog we used web scraping tools inside of R; to do that we had to use specific R packages. the main difference is that we did all the work inside the R environment. Another difference is that we had to collect the URLs we needed manually, and then parse and extract data from those URLs. Instead, incorporating the crawling process into R through the package Rcrawler we could have automatically parsed and crawled all the URLs in a specific domain. And, as shown below, we could have done all of this things in one function.

Here we tried to create a function to build a spider scraper using the Rcrawler package documentation.

```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
install.packages("Rcrawler")
library (Rcrawler)

Rcrawler(Website = "https://beppegrillo.it/",
         DIR  = "C:\Users\chiar\Desktop\Università\DAPS&CO\DATA_ACCESS\CE2_Moruzzi_Taddei", 
         RequestsDelay = 1,       # similar to Sys.sleep()
         Obeyrobots = TRUE,       # follows the instructions given by the robots.txt (allowed/not allowed parts                                     of the website to scrape)
         Useragent,               # gives information about the user
         use_proxy = NULL, 
         Encod,                   # detects the language used to program the website
         Timeout = 5,             # stops if the response doesn't come in the time specified (in this case 5                                        seconds)
         URLlenlimit = 255,       # sets maximum number of characters inside the URL (255 = default number)
         dataUrlfilter = "pattern",     # filters the parts to scrape using regular expressions
         crawlUrlfilter,                # filters the parts to crawl other URLs using regular expressions
         crawlZoneCSSPat = "p",         # works like SelectorGadget (with CSS)
         crawlZoneXPath = "pattern",         # works like SelectorGadget (with XPath)
         ignoreUrlParams,                    # doesn't consider duplicates with same content but different URLs
         KeywordsFilter = c("keyword"),      # scrapes only pages which contain the keywords (must be a vector)
         KeywordsAccuracy,                   # accuracy value is calculated using the number of matched                                                       keywords and their occurence
         FUNPageFilter,                 # filters the pages to scrape according to a specific function
         ExcludeXpathPat,               # excludes specific parts of the extracted content (using Xpath)
         ExcludeCSSPat,                 # excludes specific parts of the extracted content (using CSS)
         ExtractAsText = TRUE,          # removes HTML tags 
         ManyPerPattern = TRUE,         # if true, extracts all the parts which match the pattern; if false,                                              just the first one
         saveOnDisk = TRUE,             # if true stores downloaded contents in a specific folder
         NetworkData = FALSE,           # if true, maps the hyperlinks in the website
         statslinks = FALSE,            # counts the number of input and output links of each crawled web page
         )
```



